\Title

### 2021-03-17 latex/paper/main.tex
Fixing some typos

\begin{defn}\label{defn:energy-gain}
    Let \(\mathcal{Q}\) be an
    \(n\)-dimensional generalized cylinder.
    Let \(f : \mathcal{Q} \rightarrow \mathcal{Q}\times\R^n\) be a smoth vector
    field and let \(D \subset M\) be open.
    The system described by \(\dot{x} = f(x)\) 
    \textit{gains energy on \(D\)} if, 
    for all compact sets \(K \subset D\) and for almost every initial
    condition \(x(0) \in K\), there exists \(T > 0\) such
    that \(x(t) \notin K \, (\forall t > T)\).
    The system \textit{loses energy on \(D\)} if it gains energy in
    negative-time.
\end{defn}

@@

The notion of a nonholonomic constraint which can be stabilized via state feedback
was first described by Griffin and Grizzle in \cite{nhvc_dynamic_walking}.
Horn et. al later extended their results in
\cite{hybrid_zero_dynamics_bipedal_nhvcs} and
derived the dynamics of constrained systems.
In this section we reformulate these ideas for the Hamiltonian framework,
because the theory is cleaner when using unactuated and actuated momenta.
For this reason, we take the system of inquiry to be a Hamiltonian
mechanical system in simply actuated coordinates, as in
\eqref{eqn:simple-hamiltonian}.
For simplicity of notation, we relabel \((\tilde{q},\tilde{p})\) as \((q,p)\),
where we now have \((q,p) = (q_u,q_a,p_u,p_a)\).

@@

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}
specialize the theory of VNHCs to the acrobot. consider constraints which depend
only on pu, and show arctan vnhc and reduced dynamics. 
give definition of energy injection/dissipation. conclude with our
theorem. Make this section short and sweet.

TODO: after writing S2, re-introduce what we want to do with acrobot (energy
injection for giant stabilization)

For our model of the acrobot, we assume the acrobot iscomprised of two massless
rods of equal length \(l\), with equal point masses \(m\) at the tips.
We call this a \textit{simple} acrobot, which is displayed in Figure
\ref{fig:simple-acrobot-model}.
We will also ignore any frictional forces at both the hip and shoulder joints. 
Finally, it is important to note that a real gymnast cannot swing their legs in
full circles, though they are usually flexible enough to raise them parallel to
the floor; 
for this reason, we assume that \(q_a \in [-Q_a, Q_a]\) where 
\(Q_a \in [\frac{\pi}{2}, \pi[\).

>>>>

\begin{defn}\label{defn:energy-gain}
    Let \(\mathcal{Q}\) be an
    \(n\)-dimensional smooth manifold.
    Let \(f : \mathcal{Q} \rightarrow \mathcal{Q}\times\R^n\) be a smooth vector
    field and let \(D \subset M\) be open.
    The system described by \(\dot{x} = f(x)\) 
    \textit{gains energy on \(D\)} if, 
    for all compact sets \(K \subset D\) and for almost every initial
    condition \(x(0) \in K\), there exists \(T > 0\) such
    that \(x(t) \notin K \, (\forall t > T)\).
    The system \textit{loses energy on \(D\)} if it gains energy in
    negative-time.
\end{defn}

@@

The notion of a nonholonomic constraint which can be stabilized via state feedback
was first described by Griffin and Grizzle in \cite{nhvc_dynamic_walking}.
Horn et. al later extended their results in
\cite{hybrid_zero_dynamics_bipedal_nhvcs} and
derived the dynamics of constrained systems.
In this section we reformulate these ideas for the Hamiltonian framework,
because the theory is cleaner when using unactuated and actuated momenta.
For this reason, we take the system of inquiry to be a Hamiltonian
mechanical system in simply actuated coordinates, as in
\eqref{eqn:simple-hamiltonian}.
For simplicity of notation, we relabel \((\tilde{q},\tilde{p})\) as \((q,p)\),
where we now have \((q,p) = (q_u,q_a,p_u,p_a) \in \mathcal{Q}\times \R^n\).

@@

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}
%specialize the theory of VNHCs to the acrobot. consider constraints which depend
%only on pu, and show arctan vnhc and reduced dynamics. 
%give definition of energy injection/dissipation. conclude with our
%theorem. Make this section short and sweet.
%
%TODO: after writing S2, re-introduce what we want to do with acrobot (energy
%injection for giant stabilization)

For our model of the acrobot, we assume the acrobot is comprised of two massless
rods of equal length \(l\), with equal point masses \(m\) at the tips.
We call this a \textit{simple} acrobot, which is displayed in Figure
\ref{fig:simple-acrobot-model}.
We will also ignore any frictional forces at both the hip and shoulder joints. 
Finally, it is important to note that a real gymnast cannot swing their legs in
full circles, though they are usually flexible enough to raise them parallel to
the floor; 
for this reason, we assume that \(q_a \in [-Q_a, Q_a]\) where 
\(Q_a \in [\frac{\pi}{2}, \pi[\).
